TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-11 paper/paper.tex
Minor changes to methods

\begin{enumerate}
	\item The user owns multiple endpoints in the network. In this case a congestion algorithm is applied at both the client and server side. This scenario applies to multitentant datacenter situations, where a user owns a server in the datacenter network and a node outside of the datacenter network. In this test the user node and random node(s) are at the receiving side and the user server and random server at the sending side. The tests will be performed from a multitenant datacenter perspective.
\end{enumerate}

The created testing environment is shown in figure \ref{fig:setup1}. This is a virtual representation of the network as the client node and random node are running on one physical device. The client node and random node are listening each on a different port, which is set by the controller described in section [ENTER SECTION]. The servers are separate physical devices as one of the servers possible runs Windows when a TCP congestion control algorithm is only available for Windows. The software used for the servers and clients is Ubuntu 17.04. If Windows is used, the server will be running Windows 10.

@@

In scenario 1 the user server uses the same algorithm as the user node and the random server uses the same algorithm as the random node. Tests in this scenario cover behavioral differences between TCP congestion algorithms when a user owns a node in the network of a multitenant datacenter.

@@

\begin{table}[H]
	\centering
	\caption{Switch 1 configuration}
	\begin{tabular}[H]{ | l | l | }
	\hline
	\textbf{Hardware} & \textbf{Specification} \\
	\hline  Model & 3Com OfficeConnect Gigabit Switch 16\\
	\hline  Ports & 16x Gigabit Ethernet\\
	\hline
	\end{tabular}
	\label{table:spec2}
\end{table}

\begin{table}[H]
	\centering
	\caption{Switch 2 configuration}
	\begin{tabular}[H]{ | l | l | }
	\hline
	\textbf{Hardware} & \textbf{Specification} \\
	\hline  Model & Sitecom Gigabit Router 300N-XR\\
	\hline  Ports & 4x Gigabit Ethernet\\
	\hline
	\end{tabular}
	\label{table:spec3}
\end{table}

@@

Type some text here.

>>>>

\begin{enumerate}
	\item The user owns multiple endpoints in the network. In this case a congestion algorithm is applied at both the client and server side. This scenario applies to multitentant datacenter situations, where a user owns a server in the datacenter network and a node outside of the datacenter network. In this test the clients are at the receiving side and the user server and random server at the sending side. The tests will be performed from a multitenant datacenter perspective.
\end{enumerate}

The created testing environment is shown in figure \ref{fig:setup1}. The clients are located on one physical device and are listening each on a different port, which is set by the controller described in section [TO DO: ENTER SECTION]. The servers are separate physical devices as one of the servers possible runs Windows when a TCP congestion control algorithm is only available for Windows. The software used for the servers and clients is Ubuntu 17.04. If Windows is used, the server will be running Windows 10.

@@

In scenario 1 the user server uses the same algorithm as the first client and the random server uses the same algorithm as the second client. Tests in this scenario cover behavioral differences between TCP congestion algorithms when a user owns a node in the network of a multitenant datacenter.

@@

\begin{table}[H]
	\centering
	\caption{Switch configuration}
	\begin{tabular}[H]{ | l | l | }
	\hline
	\textbf{Hardware} & \textbf{Specification} \\
	\hline  Model & 3Com OfficeConnect Gigabit Switch 16\\
	\hline  Ports & 16x Gigabit Ethernet\\
	\hline
	\end{tabular}
	\label{table:spec2}
\end{table}

@@

TO DO: Type some text here.
